|

### 2022-12-12 r-report/Paper.Rmd

```{r,fig.cap="Figure 1"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 2"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

>>>>

```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"

source("r-analysis/data_single_polluters.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_single_polluters_stacked_rel.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_kaya_chn.R", local = TRUE, print.eval = TRUE)
